%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 
\title{ScottResume}
\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

%\lastupdated % Print the Last Updated text at the top right

\namesection{Scott}{Inan}{ % Your name
\urlstyle{same}\url{https://www.linkedin.com/in/scottinan} \\ % Your website, LinkedIn profile or other web address
\href{mailto:scott@cynicalsysadmin.com}{scott@cynicalsysadmin.com} | 408.568.7569 % Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

\section{Passions}
\descript{Infrastructure Projects}
\descript{Automation and Scripting}
\descript{All things MySQL}

\sectionspace % Some whitespace after the section
%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{Certifications}

\descript{QwikLABS AWS Solutions Architect}
\location{Associate and Professional}
\location{Completed March 2016}

\sectionspace % Some whitespace after the section

\descript{Oracle MySQL for Database Administrators}
\location{Completed October 2013}

\sectionspace % Some whitespace after the section

\descript{CompTIA A+}
\location{Completed Aug 2012}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{Valley Christian HS}

\location{Grad. 1999 | San Jose, CA}

AP Computer Science (Sophomore) \\
Junior System Administrator (97-99)

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Links
%------------------------------------------------

%\section{Links} 

%Github:// \href{https://github.com/darthschema}{\bf darthschema} \\
%LinkedIn:// \href{https://www.linkedin.com/in/scottinan}{\bf scottinan} \\
%YouTube:// \href{https://www.youtube.com/user/calmurloc}{\bf calmurloc} \\
%Facebook:// \href{https://www.facebook.com/calmurloc}{\bf calmurloc} \\
%Twitter:// \href{https://twitter.com/darthschema}{\bf @darthschema}

%\sectionspace % Some whitespace after the section

%------------------------------------------------
% Expertise \location{Over 5000 lines:}
%------------------------------------------------

\section{Expertise}

\subsection{System Administration}
Ansible \textbullet{} Puppet \textbullet{} Nagios \textbullet{} Cacti \\
LibreNMS \textbullet{} GroundWork \textbullet{} Samba4 \\
OpenVPN \textbullet{} Spacewalk \textbullet{} Zimbra \\
McAfee EPO \textbullet{} SSL \textbullet{} Asterisk \\
Active Directory \textbullet{} DNS \textbullet{} DHCP \\

\sectionspace % Some whitespace after the section

\location{Operating Systems:}
RHEL \textbullet{} CentOS \textbullet{} Debian \textbullet{} Ubuntu \\
Windows Server 2008 R2 \textbullet{} 2012 R2 \\
MacOS X \textbullet{} Solaris %\textbullet{} \\

\sectionspace % Some whitespace after the section

\location{Virtualization/Cloud:}
Xen \textbullet{} ESXi \textbullet{} EC2 \textbullet{} Rackspace \\

\sectionspace % Some whitespace after the section

\subsection{Database Administration}
MySQL \textbullet{} MariaDB \textbullet{} Galera \\
PostgreSQL \textbullet{} Oracle \textbullet{} MS-SQL \\

\sectionspace % Some whitespace after the section
\sectionspace % Some whitespace after the section

\subsection{Scripting}
BASH \textbullet{} Python \textbullet{} Perl \textbullet{} PHP \textbullet{} AHK \\
PowerShell \textbullet{} VBScript \\

\sectionspace % Some whitespace after the section
\sectionspace % Some whitespace after the section

\subsection{Development}
PHP \textbullet{} Laravel \textbullet{} CodeIgniter \textbullet{} .NET \\

\sectionspace % Some whitespace after the section


%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{University of California Observatories}
\descript{| Information Systems Manager and Administrator}

\location{July 2016 – Present | Santa Cruz, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Set up and deployed new storage cluster comprising DRBD, Corosync and MDADM to replace a variety of aging SANs.
\item Audited monitoring system (Nagios and partial Icinga migration), repaired and added needed checks - currently completing migration to Icinga2.
\item Architect a virtual core service infrastruction solution to replace all Solaris servers/services and migrate them to either Ubuntu/CentOS/Windows 2016 AD (i.e. NIS -> AD, DNS -> AD, MatLAB -> CentOS, HTTP -> Ubuntu, etc.)
\item On-site administration, setup and maintenance of Solaris, CentOS, Windows, Mac servers \& desktops including POs,  inventory management, software installs (i.e. MatLAB, IDL, Solidworks, Ansys, etc).
\item Coordinate with vendors (contracts, purchasing, etc.) and with ITS (campus IT group); and maintain documentation of all procedures, projects, automation.
\item Work with our student workers to clear away 15 years of detritus and assess our parts stock needs.
\end{tightitemize}

%\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Scratchspace Inc.}
\descript{| IT Manager}

\location{March 2015 – July 2016 | Santa Cruz, CA}
\begin{tightitemize}
\item Conducted in-depth technical analysis of all internal systems (hosted and SaaS) and made recommendations to the CEO to improve workflow and reduce cost.
\item Improved workflow by moving chat to Slack and IT task management to Asana.
\item Spearhead the cost analysis, feasibility and implementation of moving 80 of our systems to AWS and migrating our infrastructure with minimal downtime or customer impact.
\item Design / Quote HA PBXs, Nginx/PHP Webservers and Xen Virtualization clusters for customers.
\item Handle billable project management including task assignment, hour/cost tracking and report generation.
\item Assess, recommend, cleanup and document IT infrastructure for customers.
\item Perform both off and on-site maintenance and deployments for local customers utilizing Active Directory including updates, security, VPN maintenance, etc.
\item Improved both internal and customer stability and security by overhauling both monitoring (Nagios and Groundwork) and backups (Bacula) as well as performing vulnerability scans with OpenVAS.
\item Provide mentoring for System Administrators, Developers and Interns.
\end{tightitemize}

%\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Fry's Electronics}
\descript{| ISO Application Support/MySQL DBA}
%-\location{Previous positions: ISO Helpdesk/CorpTech, ISO Admin, ISO OSH}
\location{Jan 2012 – February 2015 | San Jose, CA}
\begin{tightitemize}
\item Linux and Windows Administration of a ~700 server environment across the United States and provide remote desktop support across 35 locations. 
\item Lead DBA for all MySQL databases with responsibilities including disaster recovery, point in time recovery, database security and advanced optimization. 
\item Automate processes using scripting (bash) and Puppet, develop / deploy apps like Spacewalk, Samba 4 AD DC, the current HA Zimbra cluster, and co-developed DNS/DHCP and switch/server inventory PHP web app. 
\item Worked with the EDI Administrator to troubleshoot issues and develop a new EDI application to display the records from the existing application server in a more readable format.
\item Maintain documentation for existing systems and processes for Corporate IT and remote technician and provide in-depth training for both System Administrators and Desktop Support. 
\end{tightitemize}

%\sectionspace % Some whitespace after the section
%\sectionspace % Some whitespace after the section

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE
%----------------------------------------------------------------------------------------

\newpage

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------
\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page
\section{Other Experience}
\subsection{} 
\location {OO OTR Driver}
Swift Transportation\\
Sept 2006 - Oct 2010\\
\sectionspace
\location {Tier 2 Tech Support}
Cingular Wireless\\
Oct 2004 - Aug 2006\\
\sectionspace
\location {Computer Technician}
Noah's Ark Pet Styling\\
July 2001 - Sept 2004\\
\sectionspace
\location {IT Manager}
Excelsior Manufacturing\\
Aug 1999 - July 2001\\
\sectionspace % Some whitespace after the section
%------------------------------------------------
% References
%------------------------------------------------
\section{References}
\subsection{Available on request}
\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page
%------------------------------------------------
% Projects
%------------------------------------------------

\section{Projects}

\runsubsection{Core Service Virtualization}
\descript{| Project Lead}
\location{University of California Observatories}
Replacing all core services servers (mostly Solaris SPARC servers) with VMs on 2 redundant Xen vhosts (with 2 redundant ESXi hosts for any Windows VMs needed).
\sectionspace % Some whitespace after the section

\runsubsection{Storage Cluster}
\descript{| Project Lead}
\location{University of California Observatories}
Replace existing SANs with 2 1U servers with RAID chassis so as to increase both speed and to add redundancy to our storage solution.  DRBD, Corosync, MDADM on Ubuntu 16.04 LTS used.
\sectionspace % Some whitespace after the section

\runsubsection{Cross-platform SSO}
\descript{| Project Lead}
\location{University of California Observatories}
Enhancing existing Windows and Mac SSO (via AD) by adding CentOS 6/7 servers via winbind and sssd respectively, and setting up IDMU temporarily as we work to migrate processes off NIS domain.
\sectionspace % Some whitespace after the section

\runsubsection{Network Access Control}
\descript{| Project Lead}
\location{University of California Observatories}
Setting up NAC utilizing openNAC, Foundry switches and multiple VLANs.
\sectionspace % Some whitespace after the section

\runsubsection{Zimbra Email (Open Source)}
\descript{| Project Lead}
\location{Fry's Electronics}
Migrate 2600 users from SquirrelMail to Zimbra and streamline email environment from 27 servers to 9.
\sectionspace % Some whitespace after the section

\runsubsection{MySQL Automation}
\descript{| Solo}
\location{Fry's Electronics}
Utilize scripting working towards easy maintenance of all MySQL accounts, security as well as automation of backup jobs, backup integrity checks and tuning checks.
\sectionspace % Some whitespace after the section

\runsubsection{Samba 4 AD and Windows 7}
\descript{| Project Lead}
\location{Fry's Electronics}
Deploy SMB4 Active Directory as individual trees (store and corporate) to better address workstation security and coordinate Windows 7 deployment.
\sectionspace % Some whitespace after the section

\runsubsection{Data Warehouse Migration}
\descript{| Team Member}
\location{Fry's Electronics}
Migrate data warehouse from Oracle to MySQL including automated jobs, stored procedures and backup jobs.
\sectionspace % Some whitespace after the section

\runsubsection{Spacewalk Migration/Upgrade}
\descript{| Team Member}
\location{Fry's Electronics}
Migrate DB from Oracle to PostreSQL, upgrade to Spacewalk 2 and add CentOS 6 kickstart profiles.
\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------


\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}